Optimize the Cannon 2

### 2016-10-21 paper/ms.tex
histogram_plot

$\sigma_{jn}^2$ is the data uncertainty for star n at pixel j. The number of stellar and pixel each star are N and J. Here N=548 and J = 8575. Write the objective function in the form of matrix can make it simpler. So we introduce several matrix: Y, A, C and X, which are defined as followed:

@@

By using (7) we can calculate a,b and c. b should be much bigger than both a and c. And a+b+c should be equal to 1.

The result is \(a+b+c = 0.99990\).

(a,b,c) = (-0.00215, 1.00462, -0.00258 ).

@@

 Here a,b and c are the parameters obtained from spectrum optimization. Then we infer stellar labels by using $\theta_{j}^{opt}$ and generate optimized inferred labels. The data we use is the training set, which includes 548 stellar with 8575 pixel each.
 Finally, compare the chi-squared to check whether the optimization works.

@@

 Choose four stellar, which are not in the training set:

@@

 The black line "Observed" is the observed spectrum from the data  \(y_{jn}\).
 The green line "inferred" is \( y_{j,n}^{inf}\) , which is generated by the Cannon 2.
 The red line "optimized" is \( y_{j,n}^{opt}\), which is generated by (3)
\bigskip

@@

 Finally compare the chi-square for these four stars of the two methods:
 The optimized spectrum has a 1\% smaller chi-squared so our optimization works.

 \subsection{\label{sec:level2}Experiment 2}
 Optimize $\theta_j$ and generate optimized inferred labels. Then plot the inferred labels and the optimized inferred labels.
 \bigskip

 %\includegraphics[width=170mm]{figure_3.png}
 \centerline{Fig.3 Inferred labels and the reference labels}
 \bigskip

 Finally compare the chi-square.

The chi-squared becomes 1\% bigger after the optimization. We need to do bigger optimization before inferring the labels!

>>>>

$\sigma_{jn}^2$ is the data uncertainty for star n at pixel j. The number of stellar and pixel each star are N and J. Here N and J are the number of the stellar and the number of pixel each star.  Write the objective function in the form of matrix can make it simpler. So we introduce several matrix: Y, A, C and X, which are defined as followed:

@@

By using (7) we can calculate a, b and c. b should be much bigger than both a and c. And a+b+c should be equal to 1.

@@

 Here a,b and c are parameters obtained from spectrum optimization. Then we infer stellar labels by using $\theta_{j}^{opt}$ and generate optimized inferred labels. The data we use is the training set, which includes 548 stellar with 8575 pixel each.
 Finally, compare the chi-squared to check whether the optimization works.

@@

 Choose four stellar, which are not in the training set. Optimize the spectrum of these four stars and obtain a, b and c.

 The result is \(a+b+c = 0.999\).

(a,b,c) = (0.078, 0.886, 0.035).

The values of the objective function before and after are 177254 and 174031
, which decreases by 2\%.

The labels of the four stars are:

@@

 The black line "Observed" is the observed spectrum from the data  \(y_{jn}\).
 The green line "inferred" is \( y_{j,n}^{inf}\) , which is generated by the Cannon 2.
 The red line "optimized" is \( y_{j,n}^{opt}\), which is generated by (3)

@@

Finally compare the chi-square for these four stars of the two methods:
The total chi-squared of the four stars becomes 2\% smaller, which means our method works.

 \subsection{\label{sec:level2}Experiment 2}
 Plot the parameters a, b and c vs the number of the star. 
 \bigskip

In experiment 1, we use only four stars to obtain parameters a, b and c and the result is pretty good.  What if we optimize more stars? We randomly choose about 1\% of the APOGEE DR10 and make a histogram plot. The number of stars is 639. But now parameters a, b and c are obtained from independent stars, which means the objective function only contain the chi-squared of one star and there will be 639 objective functions. And there will be 639 sets of a, b and c. Then we can plot a histogram of a, b and c to see the distribution of their values.
\bigskip

%\includegraphics[width=170mm]{figure_3.png}

Also. We plot a, b, c against the mean fiber number, which is the average fiber number of the spectrum we optimize. In APOGEE DR 10, the fiber number is between 1 and 640. The parameters we use are from $figure_3$

%\includegraphics[width=170mm]{figure_4.png}
\bigskip

This figure gives us information about the relation between parameters a, b, c and fiber number, which can be used to establish a data-driven spectrum calibration model.
